Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.Rmd
Fix alpha estimate issue

@vanderplas2021statistical suggest that $\alpha$ can be estimated using MLE with Equation \ref{eq:c-interesting-expectation}. But for precise estimate of $\alpha$, additional responses to Rorschach lineups, which is a type of lineup that consists of

plots constructed from the same null data generating mechnisam.

@@

As mentioned in Section \ref{calculating-p-values}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 lineups consist of only null plots with all combinations of $n$ and $X_{raw}$ and three replications are designed to be included in experiment III. Note that we generated the lineups using the same simulation mechanism discussed in Section \ref{sampling-from-the-null-distribution} rather than from a null model.

(it has zero effect size, an alternative to Rorschach lineups)

(Appendix: vary the alpha a little bit and see how the curves change, sensitivity analysis)

Thus, we used another valid method suggested in vanderplas2021statistical which was designed for typical lineups to estimate $\alpha$ correctly. However, by not using Rorschach lineups, we did lose some accuracy in the estimation. (questionable)

We recommend future studies to generate Rorschach lineups strictly following the definition given by buja_statistical_2009.

>>>>

@vanderplas2021statistical suggest that $\alpha$ can be estimated using MLE with Equation \ref{eq:c-interesting-expectation}. But for precise estimate of $\alpha$, additional responses to Rorschach lineups, which is a type of lineup that consists of plots constructed from the same null data generating mechanism, are required.

@@

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 lineups with all combinations of $n$ and $X_{raw}$ and three replications were included in experiment III. In these lineups, the data of the data plot was generated from a model consistent with the null hypothesis, while the data of the 19 null plots were generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. Technically, this was an alternative to Rorschach lineup but with the null distribution further conditioning on the estimated coefficients and the residual sum of squares. Thus, we used another valid method suggested in @vanderplas2021statistical which was designed for typical lineups to estimate $\alpha$. Considering the differnece between typical lineups and Rorschach lineups, we have also included a sensitivity analysis in the Appendix to examine the impact of the variance of the estimate on our findings.

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.tex
Fix alpha estimate issue

\citet{vanderplas2021statistical} suggest that \(\alpha\) can be
estimated using MLE with Equation \ref{eq:c-interesting-expectation}.
But for precise estimate of \(\alpha\), additional responses to
Rorschach lineups, which is a type of lineup that consists of

plots constructed from the same null data generating mechnisam.

@@

As mentioned in Section \ref{calculating-p-values}, \(\alpha\) used in
Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using
Rorschach lineups. Hence, 36 lineups consist of only null plots with all
combinations of \(n\) and \(X_{raw}\) and three replications are
designed to be included in experiment III. Note that we generated the
lineups using the same simulation mechanism discussed in Section
\ref{sampling-from-the-null-distribution} rather than from a null model.

(it has zero effect size, an alternative to Rorschach lineups)

(Appendix: vary the alpha a little bit and see how the curves change,
sensitivity analysis)

Thus, we used another valid method suggested in
vanderplas2021statistical which was designed for typical lineups to
estimate \(\alpha\) correctly. However, by not using Rorschach lineups,
we did lose some accuracy in the estimation. (questionable)

We recommend future studies to generate Rorschach lineups strictly
following the definition given by buja\_statistical\_2009.

>>>>

\citet{vanderplas2021statistical} suggest that \(\alpha\) can be
estimated using MLE with Equation \ref{eq:c-interesting-expectation}.
But for precise estimate of \(\alpha\), additional responses to
Rorschach lineups, which is a type of lineup that consists of plots
constructed from the same null data generating mechanism, are required.

@@

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using Rorschach lineups. Hence, 36 lineups with all
combinations of \(n\) and \(X_{raw}\) and three replications were
included in experiment III. In these lineups, the data of the data plot
was generated from a model consistent with the null hypothesis, while
the data of the 19 null plots were generated using the same simulation
method discussed in Section \ref{sampling-from-the-null-distribution}.
Technically, this was an alternative to Rorschach lineup but with the
null distribution further conditioning on the estimated coefficients and
the residual sum of squares. Thus, we used another valid method
suggested in \citet{vanderplas2021statistical} which was designed for
typical lineups to estimate \(\alpha\). Considering the differnece
between typical lineups and Rorschach lineups, we have also included a
sensitivity analysis in the Appendix to examine the impact of the
variance of the estimate on our findings.
